---
title: "Fractal snowflakes"
author: "Jasmine"
date: "23/11/2019"
output: html_document
---

```{r packages}
library(emo)
```

# Making Fractal Snowflakes `r emo::ji("snowflake")`

## Making the base of the snowflake

Picking the arms of the snowflake
- make a list of numbers 
```{r sides}
nsides <- 6

rep(0,nsides)

xstart <- rep(0,nsides)
ystart <- rep(0,nsides)
```


## angle of seperation between lines
```{r angle}
angle <- 60

firstangle <- 360/nsides*pi/180
angle <- angle*pi/180
```

## where to plot the end of your line
- think back to SOH CAH TOA
```{r making lines}
xend <- sin(firstangle*(1:nsides)) # sin = opp/hyp , OPPOSITE
yend <- cos(firstangle*(1:nsides)) # cos = adj/hyp , ADJACENT
```

## plot it!

```{r plotting}
plot.new()
# making an empty rectangle to plot on
plot(NA, xlim=c(-1,1), ylim=c(-1,1), xlab="", ylab="",
       xaxt='n', yaxt='n', asp=1)
# plot your lines in to make a *
segments(xstart, ystart, xend, yend)
```


# making this a function
```{r function}
snowflake_basic <- function(n, nsides=6, angle=60, wherebranch=0.5) {
  #draws plot background
  plot(NA, xlim=c(-1,1), ylim=c(-1,1), xlab="", ylab="",
       xaxt='n', yaxt='n', asp=1)
  
  #making the arms of the snowflake
  xstart <- rep(0,nsides)
  ystart <- rep(0,nsides)
  
  #seperation
  firstangle <- 360/nsides*pi/180
  angle <- angle*pi/180
  
  #where to plot the end of the line
  #think back to SOH CAH TOA
  xend <- sin(firstangle*(1:nsides)) # sin = opp/hyp , OPPOSITE
  yend <- cos(firstangle*(1:nsides)) # cos = adj/hyp , ADJACENT
  
  segments(xstart, ystart, xend, yend)
}

snowflake_basic()
```

## improving on the snowflake base
```{r improvement}
snowflake <- function(n, nsides=6, angle=60, wherebranch=0.5) {
  plot(NA, xlim=c(-1,1), ylim=c(-1,1), xlab="", ylab="", xaxt='n', yaxt='n', asp=1)
  xstart <- rep(0,nsides)
  ystart <- rep(0,nsides)
  firstangle <- 360/nsides*pi/180
  angle <- angle*pi/180
  xend <- sin(firstangle*(1:nsides))
  yend <- cos(firstangle*(1:nsides))
  
  last_ang <- firstangle*(1:nsides)                                                     ########
  
  segments(xstart, ystart, xend, yend)
  for(i in 2:n) {
    end_l <- (1-wherebranch)^(i-1)                                                      ########
    
    xstart <- rep(xstart + wherebranch*(xend-xstart),3)
    ystart <- rep(ystart + wherebranch*(yend-ystart),3)
    
    xend <- xstart + end_l*c(sin(last_ang-angle), sin(last_ang), sin(last_ang+angle))   ########
    yend <- ystart + end_l*c(cos(last_ang-angle), cos(last_ang), cos(last_ang+angle))   ########
    
    last_ang <- c(last_ang-angle, last_ang, last_ang+angle)                             ########
    
    segments(xstart, ystart, xend, yend)                                                ########
  }
}

snowflake(6)
```

## coloured snowflake
```{r colour}
snowflake_c <- function(n, nsides=6, angle=60, wherebranch=0.5, color=T, ...) {
  plot(NA, xlim=c(-1,1), ylim=c(-1,1), xlab="", ylab="", xaxt='n', yaxt='n', asp=1, ...=...)
  xstart <- rep(0,nsides)
  ystart <- rep(0,nsides)
  firstangle <- 360/nsides*pi/180
  angle <- angle*pi/180
  xend <- sin(firstangle*(1:nsides))
  yend <- cos(firstangle*(1:nsides))
  last_ang <- firstangle*(1:nsides)
  if(color) cols <- rainbow(n)
  else cols <- rep(1,n)
  segments(xstart, ystart, xend, yend, col=cols[1])
  for(i in 2:n) {
    end_l <- (1-wherebranch)^(i-1)
    xstart <- rep(xstart + wherebranch*(xend-xstart),3)
    ystart <- rep(ystart + wherebranch*(yend-ystart),3)
    xend <- xstart + end_l*c(sin(last_ang-angle), sin(last_ang), sin(last_ang+angle))
    yend <- ystart + end_l*c(cos(last_ang-angle), cos(last_ang), cos(last_ang+angle))
    last_ang <- c(last_ang-angle, last_ang, last_ang+angle)
    segments(xstart, ystart, xend, yend, col=cols[i])
  }
}

snowflake_c(9, angle=70, wherebranch=.45, main="FRACTAL SNOWFLAKE!!")
```


# Acknowledgements
- [Matt Tylers Tutorial](http://rpubs.com/mbtyers/239517)
- [Matt Tylers shiny app](https://mbtyers.shinyapps.io/snowflake/)
